---
title: "nihongo"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
  encoding=encoding,
  output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, message=FALSE, error=FALSE}
#add libraries
library(tidyverse)
library(knitr)
library(DT)
library(xtable)
library(kableExtra)
library(blogdown)
library(reactable)
library(shiny)

#add data tables
kanji <- read_csv("mrcollection/Kanji-Kanji 1901.csv")
sanji <- read_csv("mrcollection/KanjiSW-SwordKanji.csv")
words <- read_csv("mrcollection/Words2p8k-Words.csv")
cords <- read_csv("mrcollection/CompWords-comp.csv")
iords <- read_csv("mrcollection/IntrWords-Inter-Words.csv")
verbs <- read_csv("mrcollection/Verb500-v-list.csv")
rands <- read_csv("en_vocab_list/Complete List-Table 1.csv")
nouns <- read_csv("en_vocab_list/Adjectival nouns-Table 1.csv")
ver1s <- read_csv("en_vocab_list/Verbs-Table 1.csv")

w5rds <- read_csv("mrcollection/Word5k-Words5K.csv")
w5kds <- read_csv("mrcollection/Word5k+-Words5k.csv")

n5 <- read_csv("jlptcollection/VocabN5-N5Vocab.csv")
n4 <- read_csv("jlptcollection/VocabN4-N4Vocab.csv")
n3 <- read_csv("jlptcollection/VocabN3-N3Vocab.csv")
n2 <- read_csv("jlptcollection/VocabN2-N2Vocab.csv")

exp1 <- read_csv("jlptcollection/GoiN3-Words.csv")

jlpt <- read_csv("jlptvoc.csv")

n5grmr <- read_csv("mrcollection/N5G-GrammarN5.csv")

n5kanji <- read_csv("kanjin5n1/KanjiN5-J5.csv")
n5kanjisw <- read_csv("kanjin5n1/N5-SW.csv")

```

### **A Self Study Guide**

# {.tabset .tabset-fade .tabset-pills}
***
## Vocabulary

```{r echo=FALSE, message=FALSE, error=FALSE}

rands_1 <- rands %>% slice(0:500)
rands_2 <- rands %>% slice(501:1000)
rands_3 <- rands %>% slice(1001:1500)
rands_4 <- rands %>% slice(1501:2000)
rands_5 <- rands %>% slice(2001:2500)
rands_6 <- rands %>% slice(2501:5000)
rands_7 <- rands %>% slice(5501:9000)
rands_8 <- rands %>% slice(9001:12000)
dt_words <- sample_n(words,2800)
dt_iords <- sample_n(iords,500)
dt_cords <- sample_n(cords,500)
dt_rands_1 <- sample_n(rands_1,500)
dt_rands_2 <- sample_n(rands_2,500)
dt_rands_3 <- sample_n(rands_3,500)
dt_rands_4 <- sample_n(rands_4,500)
dt_rands_5 <- sample_n(rands_5,500)
dt_rands_6 <- sample_n(rands_6,1200)
dt_rands_7 <- sample_n(rands_7,1200)
dt_rands_8 <- sample_n(rands_8,1200)

reactable(dt_rands_1, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
reactable(dt_rands_2, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
reactable(dt_rands_3, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
reactable(dt_rands_4, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
reactable(dt_rands_5, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
reactable(dt_rands_6, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
reactable(dt_rands_7, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
reactable(dt_rands_8, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

##### **Core 2K Words:**
```{r echo=FALSE, message=FALSE, error=FALSE, message=FALSE}
reactable(dt_words, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

##### **Compound Words:**
```{r echo=FALSE, message=FALSE, error=FALSE, message=FALSE}
reactable(dt_cords, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

##### **Intermediate Words:**
```{r echo=FALSE, message=FALSE, error=FALSE, message=FALSE}
reactable(dt_iords, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

##### **Core 5K Words:**
```{r echo=FALSE, message=FALSE, error=FALSE, message=FALSE}
dt_w5rds <- sample_n(w5rds,4999)
reactable(dt_w5rds, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

##### **Core 10K Words:**
```{r echo=FALSE, message=FALSE, error=FALSE, message=FALSE}
dt_w5kds <- sample_n(w5kds,4692)
reactable(w5kds, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```


## N5 Kanji
##### **N5 Kanji:**

1|	2	|3	|4	|5	|6	|7	|8	|9	|10
-|-|-|-|-|-|-|-|-|-
人|	一|	日|	大|	年|	本|	中|	子|	見|	国
上|	分|	生|	行|	二|	間|	時|	気|	十|	女
三|	前|	入|	小|	後|	長|	下|	学|	月|	何
来|	話|	山|	高|	今|	書|	五|	名|	金|	男
外|	四|	先|	川|	東|	聞|	語|	九|	食|	八
水|	天|	木|	六|	万|	白|	七|	円|	電|	父
北|	車|	母|	半|	百|	土|	西|	読|	千|	校
右|	南|	左|	友|	火|	毎|	雨|	休|	年|	駅
道|	店|	国|	魚|	社|	新|	週|	午|	買|	会
分|	空|	安|	言|	多|	中|	見|	飲|	来|	行

##### **Kanji-Words:**
```{r echo=FALSE, message=FALSE, error=FALSE}

reactable(n5kanjisw, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```


## N4 Kanji

##### **N4 Kanji:**

1|	2	|3	|4	|5	|6	|7	|8	|9	|10
-|-|-|-|-|-|-|-|-|-
言|	手|	自|	者|	事|	思|	会|	家|	的|	方
地|	目|	場|	代|	私|	立|	物|	田|	体|	動
社|	知|	理|	同|	心|	発|	作|	新|	世|	度
明|	力|	意|	用|	主|	通|	文|	屋|	業|	特
道|	身|	不|	口|	多|	野|	考|	開|	教|	近
水|	天|	木|	六|	万|	白|	七|	円|	電|	父
北|	車|	母|	半|	百|	土|	西|	読|	千|	校
右|	南|	左|	友|	火|	毎|	雨|	休|	年|	駅
道|	店|	国|	魚|	社|	新|	週|	午|	買|	会
分|	空|	安|	言|	多|	中|	見|	飲|	来|	行

## Kanji

##### **Single Word Kanji:**
```{r echo=FALSE, message=FALSE, error=FALSE}
#dt_sanji <- sample_n(sanji,937)
reactable(sanji, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

##### **Kanji:**
```{r echo=FALSE, message=FALSE, error=FALSE}
dt_kanji <- sample_n(kanji,1901)
reactable(dt_kanji, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```



## Expressions
##### **Daily Expressions:**

    Hai. Yes. はい。  
    Iie. No. いいえ。  
    O-negai shimasu. Please. おねがいします。  
    Arigatō. Thank you. ありがとう。  
    Dōitashimashite. You're welcome. どういたしまして。  
    Sumimasen. Excuse me. すみません。  
    Gomennasai. I am sorry. ごめんなさい。  
    Ohayō gozaimasu. Good morning. おはようございます。  
    Konbanwa. Good evening. こんばんは。  
    O-yasumi nasai. Good night. おやすみなさい。

##### **Daily Life Expressions:**
```{r echo=FALSE, message=FALSE, error=FALSE}
reactable(exp1, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

    
## Nouns

```{r echo=FALSE, message=FALSE, error=FALSE, message=FALSE}

nouns_1 <- nouns %>% slice(0:500)
nouns_2 <- nouns %>% slice(501:1000)
nouns_3 <- nouns %>% slice(1001:1500)

reactable(nouns_1, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
reactable(nouns_2, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
reactable(nouns_3, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)

```

## Verbs
##### **Verb 500:**

```{r echo=FALSE, message=FALSE, error=FALSE}
dt_verbs <- sample_n(verbs,500)
reactable(verbs, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

##### **Random Verbs:**
```{r echo=FALSE, message=FALSE, error=FALSE}

ver1 <- ver1s %>% slice(0:1000)
ver2 <- ver1s %>% slice(1001:2000)
dt_ver1s <- sample_n(ver1,500)
dt_ver2s <- sample_n(ver2,500)

reactable(dt_ver1s, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
reactable(dt_ver2s, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

##### **Transitive-Intransitive Verbs:**

## Adjectives

## Adverbs

## Reading

## Grammar

##### **N5 Grammar:**
```{r echo=FALSE, message=FALSE, error=FALSE, message=FALSE}
reactable(n5grmr, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

##### **N4 Grammar:**
```{r echo=FALSE, message=FALSE, error=FALSE, message=FALSE}

```

##### **N3 Grammar:**
```{r echo=FALSE, message=FALSE, error=FALSE, message=FALSE}

```

##### **N2 Grammar:**
```{r echo=FALSE, message=FALSE, error=FALSE, message=FALSE}

```

##### **N1 Grammar:**
```{r echo=FALSE, message=FALSE, error=FALSE, message=FALSE}

```


## Conversations
##### **Daily Conversations:**

**Lesson 1**
    
    早く Hurry!	
    行きましょう Let’s go!	
    わかりました I undestand.
    どこへ Where?	
    あそこへ Over there.
    暑いですね It’s hot. Isn’t it.  
    そうですね It is. Isn’t it. 

**Lesson 2**
    
    見ましたか Did you see it?
    何を What?
    ピカソ展 Picasso Exhibition.
    まだです Not yet.
    いいですよ It’s really good.
    そうですか Really?
    明日行きます I’ll go tomorrow.

**Lesson 3**	

    おはようございます Good Morning
    おはようございます Good Morning
    パンを食べますか Would you like some bread
    食べます Yes
    コーヒーを飲みますか Would you like some coffee?
    飲みます Yes
    ビルを飲みますか Would you like some beer?	
    飲みません No
    りんごを食べますか Would you like some apple?
    それでは卵を食べますか Well then would you like some eggs?
    食べます Yes	

## Casual Conversation
##### **Daily Conversation:**
###### 1st

    今日はベランダとリビングをさらに快適にしようかなと思い Today we will improve our veranda and living room
    日よけに使うパラソルと We need a sun umbrella
    リビングで食事しやすいように And a meal-friendly table height
    ちょっと背の高いテーブルをIKEAで注文しました Ordered in Ikea
    それが今から届くので Coming Soon
    一緒に組み立てていこうかなと思います Let's Build Together
 
###### 2nd
 
    届きましたー！ So they brought our furniture!
    机さようならー Goodbye old table!
    この段ボールカッターおすすめです I advise everyone to this box knife
    Amazonを良く使う人は... For those who like us often buy on Amazon
    あ！ロシアとウクライナはあんまり Amazon使わないか Do viewers have no Amazon?
    そうだね 使わないね... Not everywhere

###### 3rd

    思ったよりちょっと暗めのグレーだね The color is darker than I thought
    本当だね Really
    ギリギリ...大きいね All is well... Big one!
    
## JLPT

##### **N5:**
```{r echo=FALSE, message=FALSE, error=FALSE}
dt_n5 <- sample_n(n5,860)
reactable(dt_n5, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

##### **N4:**
```{r echo=FALSE, message=FALSE, error=FALSE}
dt_n4 <- sample_n(n4,536)
reactable(dt_n4, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

##### **N3:**
```{r echo=FALSE, message=FALSE, error=FALSE}
dt_n3 <- sample_n(n3,1723)
reactable(dt_n3, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

##### **N2:**
```{r echo=FALSE, message=FALSE, error=FALSE}
dt_n2 <- sample_n(n2,1614)
reactable(dt_n2, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```


## N5-N1

##### **N5:**
```{r echo=FALSE, message=FALSE, error=FALSE}

jlpt_n5 <- jlpt %>% slice(2:2055)
dt_jlpt_n5 <- sample_n(jlpt_n5,2000)
reactable(dt_jlpt_n5, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE, wrap = FALSE)
```

##### **N4:**
```{r echo=FALSE, message=FALSE, error=FALSE}
jlpt_n4 <- jlpt %>% slice(2057:2724)
dt_jlpt_n4 <- sample_n(jlpt_n4,660)
reactable(dt_jlpt_n4, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE, wrap = FALSE)
```

##### **N3:**
```{r echo=FALSE, message=FALSE, error=FALSE}
jlpt_n3 <- jlpt %>% slice(2726:4864)
dt_jlpt_n3 <- sample_n(jlpt_n3,1650)
reactable(dt_jlpt_n3, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE, wrap = FALSE)
```

##### **N2:**
```{r echo=FALSE, message=FALSE, error=FALSE}
jlpt_n2 <- jlpt %>% slice(4866:6613)
dt_jlpt_n2 <- sample_n(jlpt_n2,1700)
reactable(dt_jlpt_n2, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE, wrap = FALSE)
```

##### **N1:**
```{r echo=FALSE, message=FALSE, error=FALSE}
jlpt_n1 <- jlpt %>% slice(6615:9313)
dt_jlpt_n1 <- sample_n(jlpt_n1,2200)
reactable(dt_jlpt_n1, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "courier", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE, wrap = FALSE)
```

#