---
title: "jlptn3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, message=FALSE, error=FALSE}
#add libraries
library(tidyverse)
library(knitr)
library(DT)
library(xtable)
library(kableExtra)
library(blogdown)
library(reactable)
library(shiny)

#add data tables
kanji <- read_csv("mrcollection/Kanji-Kanji 1901.csv")
sanji <- read_csv("mrcollection/KanjiSW-SwordKanji.csv")
words <- read_csv("mrcollection/Words2p8k-Words.csv")
cords <- read_csv("mrcollection/CompWords-comp.csv")
iords <- read_csv("mrcollection/IntrWords-Inter-Words.csv")
verbs <- read_csv("mrcollection/Verb500-v-list.csv")
rands <- read_csv("en_vocab_list/Complete List-Table 1.csv")
nouns <- read_csv("en_vocab_list/Adjectival nouns-Table 1.csv")
ver1s <- read_csv("en_vocab_list/Verbs-Table 1.csv")

w5rds <- read_csv("mrcollection/Word5k-Words5K.csv")
w5kds <- read_csv("mrcollection/Word5k+-Words5k.csv")

n5 <- read_csv("jlptcollection/VocabN5-N5Vocab.csv")
n4 <- read_csv("jlptcollection/VocabN4-N4Vocab.csv")
n3 <- read_csv("jlptcollection/VocabN3-N3Vocab.csv")
n2 <- read_csv("jlptcollection/VocabN2-N2Vocab.csv")

exp1 <- read_csv("jlptcollection/GoiN3-Words.csv")

```

### **A Self Study Guide**

# {.tabset .tabset-fade .tabset-pills}
***
## Words
```{r echo=FALSE, message=FALSE, error=FALSE}

rands_1 <- rands %>% slice(0:500)
rands_2 <- rands %>% slice(501:1000)
rands_3 <- rands %>% slice(1001:1500)
rands_4 <- rands %>% slice(1501:2000)
rands_5 <- rands %>% slice(2001:2500)
rands_6 <- rands %>% slice(2501:5000)
rands_7 <- rands %>% slice(5501:9000)
rands_8 <- rands %>% slice(9001:12000)
dt_words <- sample_n(words,2800)
dt_iords <- sample_n(iords,500)
dt_cords <- sample_n(cords,500)
dt_rands_1 <- sample_n(rands_1,500)
dt_rands_2 <- sample_n(rands_2,500)
dt_rands_3 <- sample_n(rands_3,500)
dt_rands_4 <- sample_n(rands_4,500)
dt_rands_5 <- sample_n(rands_5,500)
dt_rands_6 <- sample_n(rands_6,1200)
dt_rands_7 <- sample_n(rands_7,1200)
dt_rands_8 <- sample_n(rands_8,1200)

reactable(dt_rands_1, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
reactable(dt_rands_2, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
reactable(dt_rands_3, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
reactable(dt_rands_4, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
reactable(dt_rands_5, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
reactable(dt_rands_6, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
reactable(dt_rands_7, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
reactable(dt_rands_8, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

## Vocabulary

##### **Core 2K Words:**
```{r echo=FALSE, message=FALSE, error=FALSE, message=FALSE}
reactable(dt_words, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

##### **Compound Words:**
```{r echo=FALSE, message=FALSE, error=FALSE, message=FALSE}
reactable(dt_cords, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

##### **Intermediate Words:**
```{r echo=FALSE, message=FALSE, error=FALSE, message=FALSE}
reactable(dt_iords, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

##### **Core 5K Words:**
```{r echo=FALSE, message=FALSE, error=FALSE, message=FALSE}
dt_w5rds <- sample_n(w5rds,4999)
reactable(dt_w5rds, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

##### **Core 10K Words:**
```{r echo=FALSE, message=FALSE, error=FALSE, message=FALSE}
dt_w5kds <- sample_n(w5kds,4692)
reactable(w5kds, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```


## Kanji
##### **First  1901 Kanji:**
```{r echo=FALSE, message=FALSE, error=FALSE}
dt_kanji <- sample_n(kanji,1901)
reactable(dt_kanji, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

##### **Single Word Kanji:**
```{r echo=FALSE, message=FALSE, error=FALSE}
#dt_sanji <- sample_n(sanji,937)
reactable(sanji, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

## Expressions
##### **Daily Expressions:**

    Hai. Yes. はい。  
    Iie. No. いいえ。  
    O-negai shimasu. Please. おねがいします。  
    Arigatō. Thank you. ありがとう。  
    Dōitashimashite. You're welcome. どういたしまして。  
    Sumimasen. Excuse me. すみません。  
    Gomennasai. I am sorry. ごめんなさい。  
    Ohayō gozaimasu. Good morning. おはようございます。  
    Konbanwa. Good evening. こんばんは。  
    O-yasumi nasai. Good night. おやすみなさい。

##### **Daily Life Expressions:**
```{r echo=FALSE, message=FALSE, error=FALSE}
reactable(exp1, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

##### **Going-out Expressions:**
```{r echo=FALSE, message=FALSE, error=FALSE}
reactable(exp1, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

    
## Nouns

```{r echo=FALSE, message=FALSE, error=FALSE, message=FALSE}

nouns_1 <- nouns %>% slice(0:500)
nouns_2 <- nouns %>% slice(501:1000)
nouns_3 <- nouns %>% slice(1001:1500)

reactable(nouns_1, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
reactable(nouns_2, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
reactable(nouns_3, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)

```

## Verbs
##### **Verb 500:**

```{r echo=FALSE, message=FALSE, error=FALSE}
dt_verbs <- sample_n(verbs,500)
reactable(verbs, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

##### **Random Verbs:**
```{r echo=FALSE, message=FALSE, error=FALSE}

ver1 <- ver1s %>% slice(0:1000)
ver2 <- ver1s %>% slice(1001:2000)
dt_ver1s <- sample_n(ver1,500)
dt_ver2s <- sample_n(ver2,500)

reactable(dt_ver1s, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
reactable(dt_ver2s, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

## Adjectives

## Reading

## Grammar

## Conversations
##### **Daily Conversations:**
Conversation|	Translation|Structure
------------------------------------|-------------------|--------------------
**Lesson 1	第1課-th/one/lesson**	||
早く|	Hurry!	|
行きましょう|	Let’s go|	
わかりました|	I undestand|	
どこへ|	Where?|	where/[destination]
あそこへ|	Over there|	there/[destination]
暑いですね|	It’s hot. Isn’t it|	hot/it is/[agreement]
そうですね|	It is. Isn’t| it	so/it is/[agreement]
**Lesson 2	第2課-th/four/lesson-th/two/lesson**	||
見ましたか|	Did you see it?|	have seen/[question]
何を|	What?|	what/[object]
ピカソ展|	Picasso Exhibition|	Picasso-Exhibition
まだです|	Not yet|	Not yet/it is
いいですよ|	It’s really good	|really good/it is/[agreement]
そうですか|	Really?|	so it is/[question]
明日行きます|	I’ll go tomorrow|	tomorrow/go
**Lesson 3	Breakfast**	||
おはようございます|	Good Morning	|
おはようございます|	Good Morning	|
パンを食べますか|	Would you like some bread?|	bread/[object]/eat/[question]
食べます|	Yes	|eat
コーヒーを飲みますか|	Would you like some coffee?|	coffee/[object]/drink/[question]
飲みます|	Yes|	drink
ビルを飲みますか|	Would you like some beer?	|beer/[object]/drink/[question]
飲みません|	No|	not drink
りんごを食べますか|	Would you like some apple?|	apple/[object]/eat/[question]
食べませ|	No|	not eat
それでは卵を食べますか|	Well then would you like some eggs?|	so/egg/[object]/eat[question]
食べます|	Yes|	eat

## JLPT

##### **N5:**
```{r echo=FALSE, message=FALSE, error=FALSE}
dt_n5 <- sample_n(n5,860)
reactable(dt_n5, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

##### **N4:**
```{r echo=FALSE, message=FALSE, error=FALSE}
dt_n4 <- sample_n(n4,536)
reactable(dt_n4, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

##### **N3:**
```{r echo=FALSE, message=FALSE, error=FALSE}
dt_n3 <- sample_n(n3,1723)
reactable(dt_n3, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```

##### **N2:**
```{r echo=FALSE, message=FALSE, error=FALSE}
dt_n2 <- sample_n(n2,1614)
reactable(dt_n2, striped = TRUE, compact = TRUE, bordered = TRUE, style = list(fontFamily = "anonymous pro", fontSize = "13px"),highlight = TRUE, searchable = TRUE, showSortIcon = TRUE)
```


#